Adopting the Euro: a Synthetic Control Approach \\ Online Appendix\\ \vspace{2em}

### 2024-01-30 Text/Manuscript.tex
Updates from Overleaf

\begin{table}[h!]
\scriptsize
\caption{\label{TA_Gap} Doppelganger Output Gap}\centering
\begin{tabular}{lcccccccccccc} 
\toprule
 & \textbf{AUT}  & \textbf{BEL}  & \textbf{FIN}  & \textbf{FRA}  & \textbf{DEU}  & \textbf{GRC}  & \textbf{IRL}  & \textbf{ITA}  & \textbf{LUX}  & \textbf{NLD}  & \textbf{PRT}  & \textbf{ESP} \\
 \midrule  
\textbf{Gap} & \multirow{2}{*}{-682} & \multirow{2}{*}{-678} & \multirow{2}{*}{1,269} & \multirow{2}{*}{-2,843} & \multirow{2}{*}{-4,864} & \multirow{2}{*}{-153} & \multirow{2}{*}{10,961} & \multirow{2}{*}{-7,351} & \multirow{2}{*}{5,157} & \multirow{2}{*}{168} & \multirow{2}{*}{-3,706} & \multirow{2}{*}{1,539} \\
(\texteuro \ per capita) &  &  &  &  &  & &  & &  & &  &  \\
\bottomrule
\end{tabular}
\annote{This table presents the doppelganger output gap per capita in 2007. This measure is obtained by adjusting the real GDP gap for the population size and converting 2011 US dollars into 2011 euro. We use the conversion rate available from the PWT 9.1 for this year ($\approx 0.73$).}
\end{table}

@@

\begin{figure}[h!]
    \centering
    \caption{In-time Placebo Tests}
    \includegraphics[scale=1.2]{Output/Figures/SCM_normgdp_s_Rob_1992_Annual.pdf}
    \annote{In each graph, the blue dashed line represents the normalized real GDP for the synthetic country and the black full line represents the series for the actual country. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. The vertical line depicts the placebo treatment period - 1992 for all countries. For all countries, the analysis starts in 1970 and ends in 2007. %The baseline specification has as predictors labor productivity growth, employment share, and GDP shares from PENN Tables 9.1 data. OECD restricted donor pool.
    }
    \label{F_Maastricht}
\end{figure}

@@

The absence of anticipation effects for the remaining countries may be due to two things. First, the key event representing a change for most European citizens was the irrevocable exchange rate fix on 31st December 1998 and the euro launch on the 1st of January 1999. Second, most of these countries had already experienced trade and economic gains from joining the European Union \citep{Campos2018}. Therefore, such effects lie in our pre-treatment sample and thus, are already being considered.\footnote{Add the fact that Italy dropped the exchange rate agreement and floated for a year 93-94. Add that Austria and Finland joined the EU in 1995. Add that }
%Still, these figures should be analysed carefully. For example, the plot for Greece shows some effect that starts even before the placebo treatment of 1992. This anticipated effect seems to be driven by the Greek European Union (EU) accession in 1981 and not from the Euro. 
%Furthermore, estimates for Austria and Finland must be interpreted carefully as these countries entered the EU exactly in 1995 and the placebo treatment effect may be biased.

>>>>

\begin{table}[h!]
\scriptsize
\caption{\label{TA_Gap} Doppelganger Output Gap}\centering
\begin{tabular}{lcccccccccccc} 
\toprule
 & \textbf{AUT}  & \textbf{BEL}  & \textbf{FIN}  & \textbf{FRA}  & \textbf{DEU}  & \textbf{GRC}  & \textbf{IRL}  & \textbf{ITA}  & \textbf{LUX}  & \textbf{NLD}  & \textbf{PRT}  & \textbf{ESP} \\
 \midrule  
\textbf{Gap} & \multirow{2}{*}{-682} & \multirow{2}{*}{-679} & \multirow{2}{*}{1,269} & \multirow{2}{*}{-2,843} & \multirow{2}{*}{-4,864} & \multirow{2}{*}{-153} & \multirow{2}{*}{10,961} & \multirow{2}{*}{-7,351} & \multirow{2}{*}{5,157} & \multirow{2}{*}{168} & \multirow{2}{*}{-3,706} & \multirow{2}{*}{1,539} \\
(\texteuro \ per capita) &  &  &  &  &  & &  & &  & &  &  \\
\bottomrule
\end{tabular}
\annote{This table presents the doppelganger output gap per capita in 2007. This measure is obtained by adjusting the real GDP gap for the population size and converting 2011 US dollars into 2011 euro. We use the conversion rate available from the PWT 9.1 for this year ($\approx 0.73$).}
\end{table}

@@

\begin{figure}[h!]
    \centering
    \caption{In-time Placebo Tests}
    \includegraphics[scale=1.2]{Output/Figures/SCM_gdp_Rob_1992_Annual.pdf}
    \annote{In each graph, the blue dashed line represents the normalized real GDP for the synthetic country and the black full line represents the series for the actual country. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. The vertical line depicts the placebo treatment period - 1992 for all countries. For all countries, the analysis starts in 1970 and ends in 2007. %The baseline specification has as predictors labor productivity growth, employment share, and GDP shares from PENN Tables 9.1 data. OECD restricted donor pool.
    }
    \label{F_Maastricht}
\end{figure}

@@

The absence of anticipation effects for the remaining countries may be due to two things. First, the key event representing a change for most European citizens was the irrevocable exchange rate fix on 31st December 1998 and the euro launch on the 1st of January 1999. Second, most of these countries had already experienced trade and economic gains from joining the European Union \citep{Campos2018}. Therefore, such effects lie in our pre-treatment sample and thus, are already being considered.\footnote{Add the fact that Italy dropped the exchange rate agreement and floated for a year 93-94. Add that Austria and Finland joined the EU in 1995. Add that most of the divide might come from austerity measures implemented in Austria, Belgium, Finland, France, Germany, Italy \citep{Alesina2019}. Gabriel et al. 2023 ReStat, show how recessionary were these spending based austerity shocks implemented, also following the Maastricht Treaty.}
%Still, these figures should be analysed carefully. For example, the plot for Greece shows some effect that starts even before the placebo treatment of 1992. This anticipated effect seems to be driven by the Greek European Union (EU) accession in 1981 and not from the Euro. 
%Furthermore, estimates for Austria and Finland must be interpreted carefully as these countries entered the EU exactly in 1995 and the placebo treatment effect may be biased.
